---
title: "Hugo blog with RStudio and GitKraken"
author: "Eugen Bielger"
date: 2017-04-22
categories: ["R"]
tags: ["R Markdown", "GitKraken", "Hugo", "RStudio"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

# Static site generator Hugo

I was looking for something with which i can save some notes online and publish them. First i tried discourse as a well searchable knowledgebase. It was quite nice and you can get it running in a few minutes as a DigitalOcean droplet or docker container. But i'm not familiar with ruby and i need to maintain still another os. After some time i came across github pages static site generators. First i tried hubpress which was to laggy for me. Jekyll and Octopress are written in ruby 

Use it as a mailing list, discussion forum, long-form

You can embed an R code chunk like this:

```{r cars}
summary(cars)
fit <- lm(dist ~ speed, data = cars)
fit
```

# Including Plots

You can also embed plots. See Figure \@ref(fig:pie) for example:

```{r pie, fig.cap='A fancy pie chart.', tidy=FALSE}
par(mar = c(0, 1, 0, 1))
pie(
  c(280, 60, 20),
  c('Sky', 'Sunny side of pyramid', 'Shady side of pyramid'),
  col = c('#0292D8', '#F7EA39', '#C4B632'),
  init.angle = -50, border = NA
)
```
